### 2016-01-15 Docs/preface/preface.tex

\noindent \maestro\ developers (past and present) include: Ann Almgren, John
Bell, Candace Gilet, Adam Jacobs, Mike Lijewski, Chris Malone, Andy
Nonaka, Ryan Orvedahl, Charles Rendleman, \& Michael Zingale

>>>>

\noindent \maestro\ developers (past and present) include: 
\begin{quote}
Ann Almgren \\
Vince Beckner \\
John Bell \\
Max Duarte \\
Candace Gilet \\
Adam Jacobs \\
Daniel Lecoanet \\
Mike Lijewski \\
Chris Malone \\
Andy Nonaka \\
Ryan Orvedahl \\
Charles Rendleman \\
Weiqun Zhang \\
Michael Zingale
\end{quote}
